%% It is just an empty TeX file.
%% Write your code here.
\documentclass[letterpaper]{article}
\usepackage{latexsym}
\usepackage{amsbsy}
\usepackage{graphicx}
\begin{document}
\noindent
\textbf{Use Case U1S4:  Manage Countdown Time Events}\\
\textbf{Scope:  }Timer\\
\textbf{Level:  }User Goal\\
\textbf{Primary Actor:  }User\\
\textbf{Scenario:  }Enter the Countdown Time\\
\textbf{Related Use Cases:  }Use Case 1S2 \textit{The User Shall have
the Option to Stop the Countdown Timer}.\\
\textbf{Stakeholders and Interests:}
\begin{itemize}
\item User:  Wants to enter the time for the countdown.
\item User:  Wants to alter the countdown time entered as needed.
\end{itemize}
\textbf{Preconditions:  }The Countdown Timer is stopped:  (See
\textit{Use Case 1S2: The User shall have the option to Stop the
Countdown Timer}).\\
\textbf{Success Guaranties  (Postconditions)}: 
The Countdown Timer Displays the User Entered Countdown Time.\\\\
\textbf{Main Success Scenario: }\\
\begin{tabular}{|p{6cm}|p{6cm}|}\hline
\textbf{User} & \textbf{System}\\\hline
1.  Enters the Countdown Timer values in the following format:
Hours, Minutes, Seconds & \\\hline
&2.  Reads the entered time, and converts into seconds.\\\hline
&3.  Redisplays (as needed)  the entered time in \underline{proper}
Time Format.\\\hline
\end{tabular}\\\\
\textbf{Alternative Flows:  }\\
3a.  If the User enters the values that are \textit{out of bounds},
then the System displays the values in \underline{proper} format. I.E.
if the User enters ``00:67:35", the System will display:  ``1:07:35",
if the User enters ``00:67:67", the System will display: ``1:08:07"\\\\
3b.  If the User enters a \textit{typical or proper} value, then the
System will display the value as entered. ``1:45:56" will be displayed
as:  ``1:45:56".\\\\
\textbf{Technology and Variations List:  }\\
2a.  Is the input value required to be converted into seconds? Or, can the
time value be stored in the "proper" (HH:MM:SS format)?\\\\
\textbf{Frequency of Occurrence:  }Multiple Countdown Timers as
needed.\\
On a single Countdown Timer, as often as the User deisres.\\\\
\textbf{Open Issues:  }
None
\end{document}
