%% It is just an empty TeX file.
%% Write your code here.
\documentclass[letterpaper]{article}
\usepackage{latexsym}
\usepackage{amsbsy}
\usepackage{graphicx}
\begin{document}
\noindent
\textbf{Use Case U1S2:  Manage Countdown Time Events}\\
\textbf{Scope:  }Timer\\
\textbf{Level:  }User Goal\\
\textbf{Primary Actor:  }User\\
\textbf{Scenario:  }Stop the Countdown Timer\\
\textbf{Related Use Cases:  }N/A\\
\textbf{Stakeholders and Interests:}
\begin{itemize}
\item User:  Wants to stop the Countdown Timer to ensure the time is
accurate
\end{itemize}
\textbf{Preconditions:  }The Countdown Timer is up and Running:  (See
\textit{Use Case 1S4:  User Enters the Countdown Time}).\\
\textbf{Success Guaranties  (Postconditions)}: 
The Countdown Timer is stopped, the countdown time (when stopped),
is displayed (accuracy within one second).\\\\
\textbf{Main Success Scenario: }\\\\
\begin{tabular}{|p{6cm}|p{6cm}|}\hline
\textbf{User} & \textbf{System}\\\hline
1.  Indicates to stop the timing countdown. & \\\hline
&2.  Stops the countdown.\\\hline
&3.  Displays the latest countdown time.\\\hline
\end{tabular}\\\\
\textbf{Alternative Flows:  }\\
2a. If the Countdown Timer is at 0, then the Countdown Timer stops
automatically, and without User intervention.\\
3a. If the Countdown Timer is at 0, then the Countdown Timer displays
the current time of 0, and does not continue (see Alternative Flow
\textbf{2a}).\\\\
\textbf{Technology and Variations List:  }\\
2b-3b.  The Actual accuracy of the timer is dependant and
will vary based on the task schdulers of both the Operating
System and the language used for implementation.\\\\
\textbf{Frequency of Occurrence:  }Multiple Countdown Timers as
needed.\\
Multiple Countdown stops per a single Countdown Timer as the User
desires.\\\\
\textbf{Open Issues:  }
\begin{itemize}
\item What is the resolution of the Countdown Timer? One Second? A tenth of a
Second?
\item What happens if the Countdown Timer stops ``mid-resolution"? I.E.
if the Countdown Timer has a 1-second resolution, and the User stops
the Countdown Timer \textit{between} that resolution (the Countdown
Timer is between seconds, and the User stops the countdown), how is
that countdown time displayed?
\item If the Countdown Timer has one second resolution, and the user
stops say between 8 and 9 seconds, what is displayed?
\underline{8 seconds}, \underline{9 seconds}, \underline{8.323 seconds}
(time with some type of \textit{higher} resolution)???
\end{itemize}
\end{document}
