%% It is just an empty TeX file.
%% Write your code here.
\documentclass[letterpaper]{article}
\usepackage{latexsym}
\usepackage{amsbsy}
\usepackage{graphicx}
\begin{document}
\noindent
\textbf{Use Case U1S3:  Time Events}\\
\textbf{Scope:  }Timer\\
\textbf{Level:  }User Goal\\
\textbf{Primary Actor:  }User\\
\textbf{Scenario:  }Lap Timing\\
\textbf{Related Use Cases:  }Use Case 1 Scenario 1:
\textit{Start the Timing}\\
\textbf{Stakeholders and Interests:}
\begin{itemize}
\item User:  Wants to measure the measure the interval of a given
timing event.
\item User:  Wants to record the interval of a given timing event.
\end{itemize}
\textbf{Preconditions:  }The Timer started at some previous
point by the User.\\
\textbf{Success Guaranties:  (Postconditions)} 
The Timer records the lap (interval), indicates that to the User,
while continuing to meausure the complete event time.\\\\
\textbf{Main Success Scenario: }\\\\
\begin{tabular}{|p{6cm}|p{6cm}|}\hline
\textbf{User} & \textbf{System}\\\hline
1.  Indicates to lap a timing interval. & \\\hline
&2.  Calculates the elapsed time interval\\\hline
&3.  Records the Interval from the last lapped interval if there
is one, or the start of the timing event if there is no previous
interval\\\hline
&4.  Displays the Interval Elapsed time in milliseconds
resolution.\\\hline
&5.  Displays the elapsed time in seconds resolution. (See
\textit{Use Case 1S1: Start Timing})\\\hline
\end{tabular}\\\\
\textbf{Alternative Flows:  }\\
*a.  If at any time, the System cannot measure the time for the
elapsed time, then the System informs the User the Timer has
stopped working properly.\\
*b.  The User has the option to perform as many lap intervals as
desired, to the limits of the System.  The System will calculate
the interval from the \underline{previous lap interval}, not the
start of the timing event (See \textit{Step 3}).\\\\
\textbf{Technology and Variations List:  }\\
2c-5c.  The Actual accuracy of the timer is dependant and
will vary based on the task schedulers of both the Operating
System and the language used for implementation.\\
\textbf{Frequency of Occurrence:  }System should be able to record
as many lap events as needed, or until the System runs out of 
memory.\\\\
\textbf{Open Issues:  }\\
\begin{itemize}
\item Is the accuracy dependant on the Operating System?
\item Is the accuracy dependant on the Hardware?
\item How does language affect the accuracy of the Timer?
\item How does a ``fully loaded System" affect the accuracy
of the Timer?
\item Consider lapping from the start of the timing event?
\item The number of lapping events a system can handle is not
infinite and may not be able to handle as many as the User desires.
\end{itemize}
\end{document}
